An Empirical Analysis of the Role of Energy in Economic Growth

### 2014-02-10 EconGrowth2.Rnw
Removed last vestiges of X and U. Closes Issue #32.

To assess energy-augmented models of economic growth along the 
coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
historical data for economic output ($Y$), capital stock ($K$), 
labor ($L$), thermal energy ($Q$), exergy ($X$), and useful work ($U$) 
are required. Subsections below describe sources for and calculations 
to obtain historical data. A final subsection presents the historical 
data in graphical form.

>>>>

To assess energy-augmented models of economic growth along the 
coordinates of analysis outlined in Section~\ref{sec:Coordinates}, 
historical data for economic output ($Y$), capital stock ($K$), 
labor ($L$), and thermal energy ($Q$)   %, exergy ($X$), and useful work ($U$) 
are required. Subsections below describe sources for and calculations 
to obtain historical data. A final subsection presents the historical 
data in graphical form.
